\clearpage
\section{Intended Use}
\label{sec:iur}

Intended use requirements are defined using the following story format: \\
\hspace*{1.5cm}\emph{As a $<$type of user$>$, I want $<$some goal$>$ so that
$<$some reason$>$}

\begin{description}[leftmargin=5em,style=nextline]

\item[IUR-000] As a developer, I want to configure a Git client appropriate to
  my operating system so that I can interact with Git server. 

\item[IUR-001] As
  a developer, I want to create and modify a local repository so that I can
  backup my daily work products.

\item[IUR-002] As a developer, I want to add, modify and delete files from
  a local repository so that I can preserve my daily work products.

\item[IUR-003] As a developer, I want to obtain files from a remote repository
  so that I can synchronize my work with my team mates.
\item[IUR-004] As a developer, I want to annotate changes made to a local
  repository so that I track my work products.

\item[IUR-005] As a developer,
  I want to isolate my work products so that I can work on multiple assignments
  concurrently.

\item[IUR-006] As a developer, I want know the status of my local repository so
  that I can determine the state of my work products with respect to revision
  control.

\item[IUR-007] As a developer, I want to share my work products with
  other developers so that I can support team collaboration.

\item[IUR-008] As a developer, I want to know the difference between my local
  repository and a remote repository so that I can correctly integrate my work
  with the work of others.

\item[IUR-009] As a developer, I want to apply a tag
  to a git-commit so that I can re-create a branch by tag.

\item[IUR-010] As an operations personnel, I want to use a source control system
  to manage and track relevant system state and configuration within a device.

\end{description}
